Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-03-09 paper.qmd
use png for cubes plot; impact density probability

@@

```{r densities}
#| out-width: "120%"
#| echo: false
knitr::include_graphics("media/figures/cubes.pdf")
```

>>>>

# Method

From Equation 15 in [@patera2008], the impact (on the ground)
probability density, $\sigma(L, i)$, at latitude $L$ of a reentring object
whose orbit has inclination $i$ is given by:

$$ \sigma(L, i) = \frac{1}{2 \pi^2 R^2 \sqrt{(\sin^2(i) - \sin^2(L))}}$$

where $R$ is the Earth's radius.

@@

```{r densities}
#| out-width: "120%"
#| echo: false
knitr::include_graphics("media/figures/cubes.png")
```
